% !TEX program = lualatex
%----------------------------------------------------------------------------------------
%   PACKAGES AND DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[11pt,a4paper]{article}

% Geometry to maximize space while keeping it readable
\usepackage[left=0.4in,top=0.3in,right=0.4in,bottom=0.3in]{geometry}

% Font and Language Setup (Standard Protocol)
\usepackage{fontspec}
\usepackage[english]{babel}
\babelprovide[import, onchar=ids fonts]{english}

% ---------------------------------------------------------------------------------------
% FONT CONFIGURATION
% ---------------------------------------------------------------------------------------
% NOTE: This preview environment supports only the Noto family.
% TO USE WORK SANS LOCALLY:
% 1. Ensure the "Work Sans" font is installed on your system.
% 2. Comment out the \babelfont lines below.
% 3. Uncomment the \setmainfont block.

\setmainfont[
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]{RetniSans.ttf}

% Defaulting to Noto Sans for this preview:
% \babelfont{rm}{Noto Sans}
% \babelfont{sf}{Noto Sans}
% ---------------------------------------------------------------------------------------

% URL styling
\usepackage[hidelinks]{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
}

% Formatting tools
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{titlesec}

% Turn off page numbering
\pagenumbering{gobble}

%----------------------------------------------------------------------------------------
%   CUSTOM COMMANDS FOR RESUME STRUCTURE
%----------------------------------------------------------------------------------------

% Header Name
\newcommand{\name}[1]{
  \centerline{\Huge\bfseries #1}
  \vspace{0.5em}
}

% Header Contact
\newcommand{\contact}[1]{
  \centerline{#1}
  \vspace{0.5em}
}

% Section Heading
\titleformat{\section}
{\Large\bfseries\uppercase} % format
{}                          % label
{0em}                       % sep
{}                          % before-code
[\titlerule]                % after-code

\titlespacing*{\section}{0pt}{10pt}{5pt}

% Project/Experience Subsection
% Usage: \project{Title}{Link/Location}{Tech Stack}{Date/Duration}
\newcommand{\project}[4]{
  \noindent\textbf{#1} \hfill #2 \\
  \ifx&#3&%
  \else%
  \textit{#3} \hfill #4 \\
  \fi
}

% Tighter itemize for lists
\setlist[itemize]{
  noitemsep,
  topsep=0pt,
  parsep=0pt,
  partopsep=0pt,
  leftmargin=1.2em,
  label={\textbullet}
}

% Slightly tighter vertical spacing
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\setlength{\intextsep}{4pt}
\setlength{\textfloatsep}{6pt}
\setlength{\abovedisplayskip}{4pt}
\setlength{\belowdisplayskip}{4pt}

% Slightly tighter vertical spacing
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\setlength{\intextsep}{4pt}
\setlength{\textfloatsep}{6pt}
\setlength{\abovedisplayskip}{4pt}
\setlength{\belowdisplayskip}{4pt}

%----------------------------------------------------------------------------------------
%   DOCUMENT CONTENT
%----------------------------------------------------------------------------------------

\begin{document}

% HEADER
\name{Nayeem Fardin}
\contact{01616839482 \textbullet{} nayeemfardin00@gmail.com \textbullet{} \href{https://www.linkedin.com/in/nayeem-fardin-bb902a202/}{LinkedIn}}

% EDUCATION
\section{Education}
\noindent
\textbf{Bachelor of Science in Computer Science and Engineering} \hfill Expected Sep 2026 \\ 
Islamic University of Technology (IUT)

% SKILLS (Compressed to save vertical space)
\section{Skills and Interests}

\begin{tabular}{@{} >{\bfseries}l @{\hspace{1.5ex}} l @{\hspace{3ex}} >{\bfseries}l @{\hspace{1.5ex}} l @{}}
  Languages & Python, JavaScript, C++, Java & Databases & PostgreSQL, Redis, InfluxDB, Pinecone, MongoDB \\
  Web \& API & React, Node, Express, FastAPI & Cloud \& Ops & AWS, Docker, Kubernetes, Terraform, Linux, Git \\
  AI \& ML & LangChain, PyTorch, RAG, OpenAI & Sys \& Tools & Kafka, RabbitMQ, Celery, Grafana, ArgoCD, Helm \\
\end{tabular}

% PROJECTS
\section{Projects}

% --- Project 1 ---
\project{ShelfWatch}{\href{https://github.com/NFRohan/ShelfWatch}{Github}}{Python, YOLOv11, AWS, FastAPI, Docker, ONNX, Prometheus, ArgoCD, Helm, PLG Stack}{2026}
\begin{itemize}
  \item Fine-tuned and deployed \textbf{YOLOv11} on \textbf{AWS EKS} for dense retail product detection.
  \item Scalable inference service on \textbf{AWS EKS} using \textbf{Helm} + \textbf{ArgoCD} (GitOps-driven deployments).
  \item \textbf{4$\times$} CPU inference speedup and \textbf{70-90\%} cost savings via \textbf{INT8 quantization}, \textbf{AMX} and \textbf{Spot} diversification.
  \item Canary releases with \textbf{Argo Rollouts} + smoke tests; \textbf{loki/Prometheus/Grafana} for logging and observability.
  \item DevSecOps in \textbf{GitHub Actions} with \textbf{Trivy} and \textbf{pip-audit} for secure \textbf{ECR} promotion.
\end{itemize}
\vspace{3pt}

% --- Project 2 ---
\project{PixTools}{\href{https://github.com/NFRohan/PixTools}{Github}}{FastAPI, Celery, RabbitMQ, Terraform, AWS, K3s, Redis}{2026}
\begin{itemize}
  \item Architected a dual-node K3s cluster on \textbf{AWS} (On-Demand control plane + Spot data plane) with full \textbf{Terraform} IaC and automated SSM reconciliation for async image processing queued through \textbf{RabbitMQ}. 
  \item Optimized cost with \textbf{EC2 Spot} and graceful eviction via \textbf{AWS Node Termination Handler}.
  \item Resilience under load with \textbf{Redis} idempotency keys, \textbf{pybreaker} circuit breakers, and \textbf{k6} stress tests.
  \item Zero-Trust \textbf{GitHub Actions (OIDC)} CI/CD; telemetry and traces to \textbf{Grafana LGTM} via \textbf{Alloy}.
  \item Decoupled ML inference from fast conversions via dedicated queues to prevent worker starvation.
\end{itemize}
\vspace{3pt}

% --- Project 3 ---
\project{StatusMonitor}{\href{https://github.com/NFRohan/statusmonitor}{Github}}{FastAPI, React 19, Apache Kafka, InfluxDB, PostgreSQL, Docker}{2025}
\begin{itemize}
  \item Distributed monitoring platform with \textbf{FastAPI} microservices (ingestion/auth/alerting) across \textbf{Docker}, \\ designed for independent scaling.
  \item Windows agent (\textbf{psutil} + \textbf{PDH}) streaming metrics via \textbf{Kafka} to decouple producers/consumers.
  \item Reduced alert noise with in-memory cooldowns; real-time \textbf{Telegram} alerts + full history for auditability.
  \item Lowered storage cost using \textbf{InfluxDB} downsampling + tiered retention; secured onboarding with \textbf{Argon2} + \textbf{JWT} (short-lived refresh).
\end{itemize}
\vspace{3pt}

% --- Project 4 ---
\project{Crawler RAG DocHelper}{\href{https://github.com/NFRohan/crawler-rag-dochelper}{Github}}{Python, LangChain, Pinecone, Gemini 2.5, Cohere}{2025}
\begin{itemize}
  \item Hybrid-search RAG for docs using \textbf{Semantic} (HuggingFace) + \textbf{Keyword} (BM25) retrieval in \textbf{Pinecone} to boost relevance.
  \item Automated ingestion by crawling \texttt{llms.txt} via \textbf{Tavily} with caching to avoid redundant fetches.
  \item Added \textbf{Cohere Rerank} before \textbf{Gemini 2.5} generation to reduce noisy context.
  \item Exposed query-time alpha-weighting to tune keyword precision vs semantic recall.
\end{itemize}
\vspace{3pt}

% EXPERIENCE / INTERNSHIP
\section{Internship / Trainings}

\project{CyberSecurity Internship}{Backdoor Private Limited}{}{October 2025}
\begin{itemize}
  \item Digital forensics analysis to recover sensitive deleted artifacts using \textbf{FTK Imager} and \textbf{Autopsy}.
  \item Security assessments on Android applications via \textbf{MobSF} and web platforms using \textbf{Burp Suite} and \textbf{SQLMap}.

\end{itemize}

\end{document}
